Report on laboratory assignments 1 and 2 for EDA282, \\ Parallel Computer Organization and Design

### 2014-10-14 lab/report/include/lab1.tex
corrected

\todo[inline]{change}
In the producer consumer benchmark, the reading threads transition the data element to the E state if the writing thread have not accessed it already when accessing the array for the first time or when fetching it from higher level caches. However, the whole counter array is shared and thus will not state E be of any gain. Therefore, MSI and MESI performs equally regardless of working set size, which is shown in \reffig{fig:lab1bars}.

>>>>

In the producer consumer benchmark, the E state is beneficial if the writing thread accesses the data element for the first time or when it has been fetched from higher level caches. Then, the thread will transition the data element from I to M through E, when performing an increment. This avoids the S state, which give an increased performance as no bus command has to be issued. However, the probability that the writing thread accesses the data first is low, $\frac{1}{nthreads}$, which is shown in \reffig{fig:lab1bars} where MSI and MESI seems to perform equally. As the working set size increases, the benefit of the E state increases due to more frequent reads from globally invalid cache lines. This can however not be seen in the simulation results, due to fluctuations.
